Effective Reionization Likelihood from Planck 2018 Data (?)

### 2020-12-03 paper/rei.tex

\begin{figure*}
\includegraphics[width=0.7\textwidth]{plots/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite_srollv2_1015_wTauTrajectory_pl15_wTanhML.png}
\caption{Constraints from Planck data on the amplitudes of the five reionization principal components that describe all physical ionization models up to $z_{\rm max} = 30$. We show in red the Planck 2015 and the improved Planck 2018 contours in blue which uses the low-$\ell$ $EE$ likelihood \texttt{srollv2}. The 1D posterior distributions are shown on the diagonal and the 2D 68\% and 95\% C.L. regions in the $m_a-m_b$ planes in the lower triangle. The physicality priors on the ionization history used in this work are delineated by the box boundaries. [TODO: update legend] [Add text: The black solid line indicates the steplike models varying $\tau$. make point that tanh ML is now within the the center of PC constraints]}
\label{fig:plot_mjs_2018_vs_2015}
\end{figure*}
%results/pc_results/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite.pdf
%
In Fig.~\ref{fig:plot_mjs_2018_vs_2015}, we show the 1D posterior and 2D 68\% and 95\% confidence level contours for the 5 PC amplitudes that describe ionization models up to $\zmax=30$. The box boundaries correspond to the physicality priors shown in Eq.~\ref{eq:individualprior} and include all physical models along with some unphysical models. Results using the Planck 2018 data are shown in blue. While all five PC amplitudes are being constrained by Planck, the first two are particularly well-constrained. Contrary to the Planck 2015 results of Ref.~\cite{Heinrich:2016ojb} shown in red, the 2018 data prefers a much smaller amplitude for the first PC, leading to a reduced optical depth.
The trajectories shown in black lines are the steplike models of instantaneous reionization allowed by the Planck 2015 data with the arrow pointing in the direction of increasing optical depth. Clearly, these steplikes models are only a part of the allowed physical model space. By construction, they miss any high-redshift ionization component by assuming neglibile ionization levels before the transition redshift $z_{\rm re}$.

@@

>>>>

\begin{figure*}
%\includegraphics[width=0.7\textwidth]{plots/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite_srollv2_1015_wTauTrajectory_pl15_wTanhML.png}
\includegraphics[width=1.0\textwidth]{paper/plots/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite_srollv2_1015_wTauTrajectory_pl15_wTanhML_wGaussEllipse.pdf}

\caption{Constraints from Planck data on the amplitudes of the five reionization principal components that describe all physical ionization models up to $z_{\rm max} = 30$. We show in red the Planck 2015 and the improved Planck 2018 contours in blue which uses the low-$\ell$ $EE$ likelihood \texttt{srollv2}. The 1D posterior distributions are shown on the diagonal and the 2D 68\% and 95\% C.L. regions in the $m_a-m_b$ planes in the lower triangle. The physicality priors on the ionization history used in this work are delineated by the box boundaries. [TODO: update legend] [Add text: The black solid line indicates the steplike models varying $\tau$. make point that tanh ML is now within the the center of PC constraints]}
\label{fig:plot_mjs_2018_vs_2015}
\end{figure*}
%results/pc_results/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite.pdf
%
In Fig.~\ref{fig:plot_mjs_2018_vs_2015}, we show the 1D posterior and 2D 68\% and 95\% confidence level contours for the 5 PC amplitudes that describe ionization models up to $\zmax=30$. The box boundaries correspond to the physicality priors shown in Eq.~\ref{eq:individualprior} and include all physical models along with some unphysical models. Results using the Planck 2018 data are shown in blue. While all five PC amplitudes are being constrained by Planck, the first two are particularly well-constrained. Contrary to the Planck 2015 results of Ref.~\cite{Heinrich:2016ojb} shown in red, the 2018 data prefers a much smaller amplitude for the first PC, leading to a reduced optical depth.
The trajectories shown in black lines are the steplike models of instantaneous reionization allowed by the Planck 2015 data with the arrow pointing in the direction of increasing optical depth. Clearly, these steplikes models are only a part of the allowed physical model space. By construction, they miss any high-redshift ionization component by assuming neglibile ionization levels before the transition redshift $z_{\rm re}$.

@@

\begin{figure}
\includegraphics[width=0.40\textwidth]{plots/pl18_tanh_highz_kde_f0p14_tau_z_to_zstart_plot_tau_gtz_dz0p1.pdf}
\caption{
}
\label{fig:plot_taugtz_two_step_contours}
\end{figure}
